Contextual Identity: A Framework for Usable Privacy

### 2012-10-13 paper.tex
copy-edited whole thing, added expiring contextual identities section

Helen Nissenbaum has long argued that privacy violations come not from the
simple sharing of personal information, but rather from sharing that
information in a way that violates social norms, or in the wrong
context~\cite{nissenbaum}. The desire for spontaneous, positive human
interaction often necessitates sharing personal information. Take, for example,
PatientsLikeMe~\cite{patientslikeme}. This site functions as a support group
and also a place for people to share health information, such as drug regimens,
treatment history, side-effects, and more. Though this information is
traditionally considered extremely sensitive, the users of this site clearly
consider the benefits of sharing (longitudinal graphs of their own health
history, building community with people who share their disease) to outweigh
the privacy risks. So long as the contextual integrity of the shared data is
kept intact, users will continue to trust and use the site. Selling user data
intended for one purpose for another (e.g., to insurance companies to discover
uninsurable patients) would be a clear violation of that expectation.
%this story is a positive story to shock security folk with the breadth and
%depth of personal information that ordinary users will share
% instead we could lead with a shocking, negative story like how gay youth get
% killed when they're outed

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually what forget.  However, with the advent of increasingly vast
searching, indexing, and archiving cabilities, one cannot rely on forgetting in
online enviroments~\cite{delete}. Thus, managing contextual identities in
online environments has become increasingly difficult and fraught with
mistakes.

@@

We provide a simple formalization of the notion of contextual identity, use it as a
framework to understand existing privacy violations, and analyze mitigations to
those violations.

@@

Many authors have discovered attacks to link different contextual identities to
the same person. Narayanan and Shmatikov present a re-identification technique
to merge anonymized social graphs from different networks and prove that
Netflix and IMDB and Flickr and Twitter can be
linked~\cite{narayanan1,narayanan2}. Lindamood et al.~and Mislove et al.~show
how to infer previously undisclosed information from released social networking
data~\cite{lindamood,mislove}.

@@

Although network attacks are very powerful, at the current time they require a
level of expertise and resources not typically held by those causing the most
worry to users. A brief survey of social networking advice reveals that the
major causes of concern come not from a dedicated graph expert, but people
close to the user: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
Surveys conducted by Wang et al.~show that typical regrets from posting on
Facebook stem almost exclusively from fear of negative interactions with people
that the users knows~\cite{wang}. The consequences of these negative
interactions can lead to loss of employment or breaking personal relationships.
Most previous privacy research has focused on distant adversaries, where the
bad actor is a behavioral tracking service, state agent or unknown
eavesdropper; in contrast, we assert that users care more about their
interactions with others close to them.

@@

A user may have multiple contextual identites $\{I\}$. These identities change
over time, as users form and dissolve relationships, and focus on different
sets of tasks. The user's goal is to accomplish tasks in $T$,
interact with those in $R$ and claim to be $p$  while being able to predict and
assert control over as much of $I$ as possible.

Our definition focuses on relationships because most privacy concerns stem
from causing an unexpected exchange of data with people the users
knows~\cite{wang}. Tasks are key because users are task-oriented, and it is
easy to map user actions (page navigation, sending email, posting, filling
forms) to tasks.  The definition of $R$ is deliberately underspecified, as this
is work in progress.

\begin{definition}
  A Contextual Identity Violation occurs when a user's contextual identity
parameters $R,T,p$ are controlled by others.  When a user's tasks are shared
with the wrong set $R$, the wrong projected identifier $p$ is employed, or a
user is perceivied as undertaking a set of tasks $T$ they do not anticipate, a
violation of the integrity of Contextual Identity occurs.

@@

\section{Contextual identity violations}
\label{sec:examples}
\subsection{Redistributing information out of context}
(Lack of control over $R$).\\
Re-distributing information out of its original context often leads to
embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
third-party sites to publish purchases, travel bookings, movie rentals to the
user's activity stream.  Because of poor opt-out and lack of visibility into
what was being published, user outcry was immediate~\cite{mccarthy,nakashima}.
In December 2007, Google Reader exposed RSS feeds of user-marked news stories
to the user's Google Talk contacts\footnote{Google Talk contacts are everyone
with whom a user has chatted, which might include co-workers, supervisors, and
friends}. Although this feed was always public, prior to this launch it was not
discoverable, leading to a bad experience for many users~\cite{helft}. In
February 2010, Google Buzz launched, a product that
exposed the user's most frequent Gmail and Google Talk contacts and their
publicly available (through previously less discoverable) news and photos.  The
combination of exposing contacts (which could include abusive ex-husbands,
co-workers, and friends), as well as aggressively linking photos and news
items, resulted in a huge backlash~\cite{fugitivus,buzz}. In September 2012,
Facebook imported old wall posts from 2008 into the new Timeline interface.
Although wall posts were always visible from profile pages, the new Timeline
interface brought old wall posts (which users used to treat as private
messages, before the advent of ``Like'' and comment buttons) to the attention
of an audience that the user never intended~\cite{timeline}.

In all these examples, the audience $R$ of the identity expanded without user
intervention.

\subsection{Unsatisfiable policies}
(Lack of control over $p$).\\
Sometimes service providers have policies which preclude isolating multiple
identites. For example, Facebook and Google have a ``Real Names'' policy, which
requires users to register for accounts with their legal
name~\cite{fb_names,google_names}.  These policies presume the users can be one
person to everyone. These policies ignore that community-building happens in
many different contexts, that users have many legitimate reasons for presenting
different identities in different contexts, and that users don't necessarily
want those identities to be linked. For example, disallowing avatar handles as
a primary identifier makes building a gaming community difficult at best, and
linking a gaming identity to a professional identity has already caused
problems for one exposed has already caused problems for Maine Senate candidate
and World of Warcraft gamer Colleen Lachowicz in 2012~\cite{maine}.

It is impossible for users who want to isolate multiple contextual identities
to participate in these networks without violating the terms of service.  The
Google ``legal name'' policy prohibits users from asserting control over $p$.

\subsection{Federated login}
(Lack of flexibility in $p$).\\
Facebook Connect is a login platform that allows third-party websites to
authenticate users using their Facebook identity~\cite{fb_connect}. Because it
is against the terms of service to have multiple Facebook accounts, using
Facebook Connect has the unwanted side-effect of linking multiple contextual
identities.

Similar to the Unsatisfiable policies, many federated login systems simply
don't have the ability to allow users multiple $p$ values, or identifiers.
Other federated login systems may support and allow multiple identifiers, but
it can be poorly implemented or difficult to discover, which essentially means
the feature isn't used.
There are some login platforms and protocols, including OAuth and BrowserID
that do not suffer from this policy or design error~\cite{browserid,oauth},
giving a user better control over which value of $p$ he employs in his
contextual identity.
\begin{comment} (TODO:
this is actually kinda complicated -- yahoo, twitter, google allow multiple
accounts but the multi-login support is broken at google, not sure how it is
with others, oauth protocol supports multiple accounts, persona clearly
supports multiple accounts)
\end{comment}

@@

Similar to DM failures, posting to the wrong account is also a common mistake.
Because many jobs require posting on social networks on behalf of the company,
many people now have multiple accounts for personal and business use.
KitchenAid, Chrysler, and Google are just three examples whose employees have
made this mistake in the past year~\cite{kitchenaid,chrysler,yegge}.

\subsection{Third party tracking}
\label{sec:tracking}
(Lack of control over $T$, and correlation across values of $p$).\\
Even if a user does not participate in social networks, they are still subject
to tracking by virtue of browsing the web. Third-party cookies, flash cookies,
web bugs, device fingerprinting, geolocation, history sniffing and more are
techniques that a dedicated third party could use to collect browsing history
and link contextual identities through correlation of tasks in $T$ for various
identity values $p$.

@@

\subsection{Inferring contextual identities}
Accurately detecting the user's current contextual identity, whether
heuristically or through asking the user, is paramount to helping the user
manage it.

Although a person's contextual identities may be subconsciously clear,
expecting users to enumerate their identities and manually curate them is
probably too burdensome. Firefox has a Profile Manager, but not many people
know about it or how to use it, to the extent that it will be
removed\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}.

Tang et al.~show that most people do not take the time to create labels and
maintain friend lists~\cite{tang}. However, the same authors show how to use
heterogenous networks to infer relationship types (e.g., manager-subordinate)
through the graph itself is unlabeled.

@@

Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
for private browsing mode, and thus interaction with extensions, treatment of
cookies, history, and bookmarks upon entering and exiting this mode are
different and serve different use cases. Depending on user desire, $R$ when
using private browsing mode may be other household members, or it may be a
service to which the user wants to limit cookie leakage. A strong contextual
identity mechanism allows users control over $R$ or over $T$ when $R$ is
clearly identified to them, but the various privacy modes in different web
browsers either allows the user control over $T$ or over $R$, but not both at
the same time.

A partial solution is to prompt the user when they're about to link
multiple contextual identities through a federated login service. For example,
Persona is the suite of tools that implements the BrowserID protocol, and it
supports multiple email identifiers~\cite{browserid}. In this case, when the
user decides to register for a service using Persona, the task $T$ they are
performing is authentication, the relationships $R$ are ones they will engage
in when using the service, and $p$ is tied to the email identifier they use to
register for the service. Because we can categorize the type of service by URL
as \texttt{aboutprofile} does, Persona could prompt the user when they're about
to link the same email identifier to radically different contextual identities,
such as ones for dating and professional use.  Persona allows the user direct
control over $p$ given a context ($R,T$) in which they're authenticating.

\begin{comment}
TODO: Discuss how private browsing mode maps to R, T, P?

At home use case:
R is household
T is porn?
P is null

Searching use case:
R is Google
T is search
P is null

GoogleShring use case
R is Google and the GoogleSharing proxy
T is search or browsing (analytics) (can't use any services that require logon)
P is random
\end{comment}

\subsection{Recovering from Mistakes}
\subsubsection{Auditing}
A major cause of user embarrassment is exposing information to the wrong
audience, as illustrated in Section~\ref{sec:examples}. A browser is in an
ideal position to intermediate social network posts, aggregate them locally,
and present them to the user when they desire to audit their digital footprint.

For example, a user could see all of the comments and posts they made in the
last week and redact content that is sensitive or too negative, topics that are
frequently regretted~\cite{wang}.  This redacting is equivalent to asserting
better control over $T$. Although this approach does not help when the service
provider decides to change the audience on the user's behalf (loss of control
over $R$), auditing gives the user a good opportunity to review posts that
might cause regrets. In the case of high-volume users, such a tool could
incorporate sentiment analysis to aid the user in finding particularly
problematic content.  This effectively helps users adjust $T$ when $R$ changes
unexpectedly; while it does not help bring users into better control over $R$,
it can help them minimize the impact of a changing $R$.

Profiles can be generated by user-supplied application-level data, but also
implicitly through browsing via techniques in Section~\ref{sec:tracking}. Collusion is a
tool for visualizing cookies~\cite{collusion}, in particular the third-party
cookies set by tracking sites which are typically ad networks.  Once the user
knows which sites are tracking them, they can choose to block cookies from
those sites.  This type of tool allows users good control over $R$ by limiting
who sees the tracks they create.

\subsubsection{Remembering to Forget}
Humans don't have perfect memories, and one could argue that social
networks should also forget~\cite{delete}. Many users already engage in manual auditing and
deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
that let the user manage this more easily through an API: both Twitter and Facebook provide
APIs for deletion\footnote{At the time of this writing, Google Plus offers a
read-only API}. One way to reduce the likelihood of linked contextual
identities would be to provide applications that expire posts after some time.
This would help users better contain the whole context ($R,T$) by segmenting
one large audience and one large set of tasks into smaller temporal partitions.

@@

\subsection{Preventing Mistakes}
\subsubsection{Controlling Information Flow}
Sometimes a user might want to prevent mistakes from being made in the first
place. If a user is concerned about a particular service provider, they can
install an extension like Disconnect to disallow cookies from that provider
unless they explicitly want to interact with that site~\cite{disconnect}.
This type of tool (cookie blocker) helps users assert control over audience ($R$).

Protocols like Do Not Track are also a good first step to solving this
problem~\cite{dnt}. Although Do Not Track is unenforceable from the client
side, it provides a clear signal to service providers and ad networks
that the user does not want to be tracked. As adoption increases, ignoring this
signal will lead to loss of reputation for service providers that explicitly
act against their users' wishes.
This type of tool (cookie blocker) helps users assert control over the effects of their actions ($T$).

The Google Sharing project allows users of Google services to share and mix the way Google identifies them~\cite{googlesharing}.  The effect is that users employ a contextual identity $\{T_{gs}, R_{gs}, p\}$ with a shared $p$.  These users employ it only for Google sites ($R_{gs} = Google$) and can accomplish tasks $T_{gs}$ while associating all their actions with a random $p$ also associated with many other users.  This devalues $p$ and makes it difficult to correlate $T_{gs}$ with $T$ from another of the users' contextual identities.

@@

\begin{comment}
first party regrets, third party regrets
impossible to judge how big friends of friends
\end{comment}

\section{Open problems}
The mitigations proposed in this work become more complex in the face of shared
devices and overlapping identities. There are good reasons to want to intermix
work and personal identities (increased exposure, serendipitous connections)
and so many people use the same account for both personal and work reasons.

@@

close to you “stranger on a train” “stranger on a plane”
\end{comment}

>>>>

Helen Nissenbaum has long argued that privacy violations come not from the
simple sharing of personal information, but rather from sharing that
information in a way that violates social norms, or in the wrong
context~\cite{nissenbaum}. The desire for spontaneous, positive human
interaction often leads to sharing personal information. For example, take
PatientsLikeMe~\cite{patientslikeme}. This site functions as a support group
and as a place for people to share health information, such as drug regimens,
treatment history, side-effects, and more. Though this information is
traditionally considered extremely sensitive, the users of this site clearly
value the benefits of sharing (longitudinal graphs of their own health history,
building community with people who share their disease). Further, sharing
personal information does not mean that the users don't value privacy.  Selling
user data originally intended for one purpose for another (e.g., to insurance
companies to discover uninsurable patients) would be a gross violation of
users' privacy expectations.

%this story is a positive story to shock security folk with the breadth and
%depth of personal information that ordinary users will share
% instead we could lead with a shocking, negative story like how gay youth get
% killed when they're outed

In offline environments, managing contextual identities is more intuitive than
in online environments. There are cues to help you determine where you are,
who your intended audience is, how many people will overhear you, and how
likely your information is to be re-broadcast in a different context. It is
also true that in offline environments, humans don't have perfect memories and
will eventually what forget.  However, with the advent of increasingly vast
searching, indexing, and archiving capabilities, one cannot rely on forgetting
in online enviroments~\cite{delete}. Thus, managing contextual identities 
online has become increasingly difficult and fraught with mistakes.

@@

We provide a simple formalization of the notion of contextual identity, use it as a
framework to understand existing privacy violations, and analyze mitigations of
those violations.

@@

Many authors have discovered attacks to link different contextual identities to
the same person. Narayanan and Shmatikov present a re-identification technique
to merge anonymized social graphs from different networks and prove that
user identifiers from Netflix and IMDB and Flickr and Twitter can be
linked~\cite{narayanan1,narayanan2}. Lindamood et al.~and Mislove et al.~show
how to infer previously undisclosed information from released social networking
data~\cite{lindamood,mislove}.

@@

Although network inference and merging attacks are very powerful, at the
current time they require a level of expertise and resources not available to
most people. A brief survey of social networking
advice reveals that the
major causes of concern come not from a dedicated social graph expert, but people
close to the user: friends, family, and co-workers~\cite{fbtips2,fbtips1}.
Surveys conducted by Wang et al.~show that typical regrets from posting on
Facebook stem almost exclusively from fear of negative interactions with people
that the user knows~\cite{wang}. The consequences of these negative
interactions can lead to loss of employment or breaking personal relationships.
Most previous privacy research has focused on distant adversaries, where the
bad actor is a behavioral tracking service, state agent or unknown
eavesdropper; in contrast, we assert that users care more about their
interactions with others close to them.

@@

A user may have multiple contextual identities $\{I\}$. These identities change
over time, as users form and dissolve relationships, and focus on different
sets of tasks. The user's goal is to accomplish tasks in $T$,
interact with those in $R$ and claim to be $p$  while being able to predict and
assert control over as much of $I$ as possible.

Our definition focuses on relationships because most privacy concerns stem
from causing an unexpected exchange of data with people the users
knows~\cite{wang}. Tasks are key because users are task-oriented, and it is
easy to map user actions (page navigation, sending email, posting, filling
forms) to tasks.

\begin{definition}
  A Contextual Identity Violation occurs when
parameters $R,T,p$ are controlled by others.  When a user's tasks are shared
with the wrong set $R$, the wrong projected identifier $p$ is employed, or a
user is perceived as performing tasks $T$ they do not anticipate, a
violation of the integrity of Contextual Identity occurs.

@@

\section{Contextual identity violations}
\label{sec:examples}
\subsection{Redistributing information out of context}
(Lack of control over $R$).\\
Re-distributing information out of its original context often leads to
embarrassment~\cite{nissenbaum}.  In November 2007, Facebook Beacon allowed
third-party sites to publish purchases, travel bookings, movie rentals and more to the
user's activity stream.  Because of poor opt-out and lack of visibility into
what was being published, user outcry was immediate~\cite{mccarthy,nakashima}.
In December 2007, Google Reader exposed RSS feeds of user-marked news stories
to the user's Google Talk contacts\footnote{Google Talk contacts are everyone
with whom a user has chatted, which might include co-workers, supervisors, and
friends}. Although this feed was always public, prior to this launch it was not
discoverable, leading to a bad experience for many users~\cite{helft}. In
February 2010, Google Buzz launched, a product that
exposed the user's most frequent Gmail and Google Talk contacts and their
publicly available (through previously less discoverable) news and photos.  The
combination of exposing contacts (which could include abusive ex-husbands,
co-workers, and friends), as well as aggressively linking photos and news
items, resulted in a huge backlash~\cite{fugitivus,buzz}. In September 2012,
Facebook imported old wall posts from 2008 into the new Timeline interface.
Although wall posts were always visible from profile pages, the new Timeline
interface brought old wall posts which users used to treat as private
messages, before the advent of ``Like'' and comment buttons, to the attention
of an audience that the user never anticipated~\cite{timeline}.

In all these examples, the audience $R$ of the contextual identity expanded without user
intervention.

\subsection{Unsatisfiable policies}
\label{sec:policies}
(Lack of control over $p$).\\
Some service providers have policies which preclude isolating multiple
contextual identities. For example, Facebook and Google have a ``Real Names'' policy, which
requires users to register for accounts with their legal
name~\cite{fb_names,google_names}.  These policies presume the users can be one
person to everyone. These policies ignore that community-building happens in
many different contexts, that users have many legitimate reasons for presenting
different identities in different contexts, and that users don't necessarily
want those identities to be linked. For example, disallowing avatar handles as
a primary identifier makes building a gaming community difficult. 
Linking a gaming identity to a professional identity has already caused
problems for 2012 Maine Senate candidate
and World of Warcraft gamer Colleen Lachowicz~\cite{maine}.

It is impossible for users who want to isolate multiple contextual identities
to participate in these networks without violating the terms of service.  The
``Real Names'' policy prohibits users from asserting control over $p$.

@@

Similar to DM failures, posting to the wrong account is also a common mistake.
Because many jobs require posting on social networks on behalf of the company,
it is common to have multiple accounts for personal and business use.
KitchenAid, Chrysler, and Google are three companies whose employees have
made this mistake in the past year~\cite{kitchenaid,chrysler,yegge}.

\subsection{Federated login}
\label{sec:login}
(Lack of flexibility in $p$).\\
Facebook Connect is a login platform that allows third-party websites to
authenticate users using their Facebook identity~\cite{fb_connect}. Because it
is against the terms of service to have multiple Facebook accounts, using
Facebook Connect has the unwanted side-effect of linking multiple contextual
identities.

Similar to section~\ref{sec:policies}, many federated login systems simply
don't have the ability to allow users multiple $p$ values, or identifiers.
Other federated login systems have support for multiple identifiers, but
this feature can be poorly implemented or difficult to discover, leading to
low use.
Some login platforms and protocols, such as OAuth and BrowserID,
do not suffer from this policy or design error~\cite{browserid,oauth},
giving a user better control over which value of $p$ to employ.

\subsection{Third party tracking}
\label{sec:tracking}
(Lack of control over $T$, and correlation across values of $p$).\\
Even if a user does not participate in social networks, they are still subject
to tracking by virtue of browsing the web. Third-party cookies, flash cookies,
web bugs, device fingerprinting, geolocation, history sniffing and more are
techniques that a dedicated third party could use to collect browsing history
and link contextual identities through correlation of tasks in $T$ for various
values of $p$.

@@

\subsection{Inferring contextual identities}
Accurately detecting the user's current contextual identity, whether
heuristically or through asking the user, is paramount to helping the user
manage it.
Although a user may subconsciously be aware of their contextual identities,
expecting users to enumerate their identities and manually curate them is
probably too burdensome. Firefox has a Profile Manager, but it is so difficult to use that it will be removed.\footnote{See \url{https://bugzilla.mozilla.org/show\_bug.cgi?id=214675\#c53}}.

Tang et al.~show that most people do not take the time to create labels and
maintain friend lists~\cite{tang}. However, the same authors show how to use
heterogenous networks to infer relationship types (e.g., manager-subordinate)
though the graph itself is unlabeled.

@@

Privacy modes in Firefox, Chrome, Safari, and Opera are a good first step, but
are no means a complete solution~\cite{ABBJ10}. There is no standard behavior
for private browsing mode, and thus interaction with extensions, treatment of
cookies, history, and bookmarks upon entering and exiting this mode are
different and serve different use cases. Depending on user desire, $R$ when
using private browsing mode may be other household members, or it may be a
service to which the user wants to limit cookie leakage.
%this requires more explanation, omitting for now. A strong contextual
%identity mechanism allows users control over $R$ or over $T$ when $R$ is
%clearly identified to them, but the various privacy modes in different web
%browsers either allows the user control over $T$ or over $R$, but not both at
%the same time.

Another partial solution is to prompt the user when they're about to link
multiple contextual identities through a federated login service. For example,
Persona is the suite of tools that implements the BrowserID protocol, and it
supports multiple email identifiers~\cite{browserid}. In this case, when the
user decides to register for a service using Persona, the task $T$ they are
performing is authentication, the relationships $R$ are ones they will engage
in when using the service, and $p$ is tied to the email identifier they use to
register for the service. Because we can categorize the type of service by URL
as \texttt{about:profile} does, Persona could prompt the user when they're about
to link the same email identifier to radically different contextual identities,
such as ones for dating and professional use.  Persona allows the user direct
control over $p$ given a context {$R,T$} in which they're authenticating.

\subsection{Expiring contextual identities}
Oftentimes a user may have a long-term task, such as wedding planning or house
buying, that requires constructing a contextual identity. The tasks associated
with this identity have an externally imposed deadline and may have long-lived
side-effects, such as long-term cookies that reveal sensitive information
(e.g., the neighborhood of the house purchase, income information derived from
purchases, other demographic data). For contextual identities that have
outlived their usefulness, users would benefit from destruction of side-effects
in $T$ such as cookie data.

\subsection{Recovering from Mistakes}
\subsubsection{Auditing}
A major cause of user embarrassment is exposing information to the wrong
audience, as illustrated in section~\ref{sec:examples}. A browser is in an
ideal position to intermediate social network posts, aggregate them locally,
and present them to the user when they desire to audit their digital footprint.
For example, a user could see all of the comments and posts they made in the
last week and redact content that is sensitive or too negative, a frequent cause
of regret~\cite{wang}.  Redaction allows the user to assert
better control over $T$ as well as $p$. Although this approach does not help when the service
provider decides to change the audience on the user's behalf (loss of control
over $R$), auditing gives the user a good opportunity to review posts that
might cause regrets. In the case of high-volume users, such a tool could
incorporate sentiment analysis to aid the user in finding particularly
problematic content.  This effectively helps users adjust $T$ when $R$ changes
unexpectedly.

Profiles can be generated by user-supplied application-level data, but also
implicitly through browsing via techniques in Section~\ref{sec:tracking}. Collusion is a
tool for visualizing cookies~\cite{collusion}, in particular third-party
cookies set by tracking sites which are typically ad networks.  Once the user
knows which sites are tracking them, they can choose to block cookies from
those sites.  This type of tool allows users good control over $R$ by limiting
who sees the side-effects in $T$.

\subsubsection{Remembering to Forget}
Humans don't have perfect memories, and perhaps social
networks should not either~\cite{delete}. Many users already engage in manual auditing and
deletion of old posts~\cite{fbtips2}. A better solution would be to build tools
that let the user manage this more easily through an API: both Twitter and Facebook provide
APIs for deletion\footnote{At the time of this writing, Google Plus offers a
read-only API}. One way to reduce the likelihood of linked contextual
identities or assert better control over $p$ would be to provide applications that expire posts after some time.
Deletion ane expiration also reduce $R$ (in the case of public posts) and $T$.
%This would help users better contain the whole context ($R,T$) by segmenting
%one large audience and one large set of tasks into smaller temporal partitions.

@@

\subsection{Preventing Mistakes}
\subsubsection{Controlling Information Flow}
Sometimes a user might want to prevent mistakes from being made in the first
place. If a user is concerned about a particular service provider, they can
install an extension like Disconnect to disallow cookies from that provider
unless they explicitly want to interact with that site~\cite{disconnect}.
This type of tool (cookie blocker) helps users assert control over audience $R$.

Protocols like Do Not Track are also a good first step to solving this
problem~\cite{dnt}. Although Do Not Track is unenforceable from the client
side, it provides a clear signal to service providers and ad networks
that the user does not want to be tracked. As adoption increases, ignoring this
signal will lead to loss of reputation for service providers that explicitly
act against their users' wishes, helping
users assert control over the effects of their actions $T$.

The Google Sharing project allows users of Google services to confound the way
Google identifies them~\cite{googlesharing}.  The effect is that users employ a
contextual identity with a shared $p$.  These users
employ it only for Google sites and can accomplish tasks
while associating all their actions with a random $p$ also associated
with many other users.  This devalues $p$ and makes it difficult to correlate
tasks with a particular user.

@@

\section{Open problems}
We are largely ignorant of the ways in which users think about contextual
identity. Building usable software to manage contextual identity demands
further research.

The mitigations proposed in this work become more complex in the face of shared
devices and overlapping identities. There are good reasons to want to intermix
work and personal identities (increased exposure, serendipitous connections)
and so many people use the same account for both personal and work reasons.

@@

close to you “stranger on a train” “stranger on a plane”
first party regrets, third party regrets
impossible to judge how big friends of friends

\end{comment}
